Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-02 paper/ms.tex
update manuscript

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$ (brighter stars
    are larger). The \texttt{X} and \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale.  Two stars of
    interest are ``Star A'' and ``Star B'', which were eventually
    excluded as being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f6.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
		SOAR HRCam contrast limits derived from point-source
		injection-recovery experiments. A companion dubbed Star A ($\Delta T=4.7$,
	$2.3''$ west) is detected in the autocorrelation function,
	and is also a resolved Gaia source.  It is co-moving with
	\tn, and its parallax and on-sky position imply that it is
	physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		{\it Middle:} RV measurements, with best-fit instrument offsets
	and jitter terms included.  The expected scatter from starspots
	based on $v\sin i$ and the photometric modulation amplitude is of
	order 300m$\,$s$^{-1}$.
	{\it Bottom:}
	RV measurements phased to the orbital ephemeris of \pn.  The
	planet is not detected.  The black line shows a circular
	Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{RVs}
The combined radial velocities from FEROS, CHIRON, and Veloce can be
used to place limits on the presence of massive, close-in bound
companion to \tn.  We derived the relevant limits using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits for the companion, and performed two sets of fits.

@@

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
However, unlike these planets, \pn\ is validated but not yet
confirmed.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{winn_exoplanet_2010}
\begin{equation}
  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 21\,{\rm m\,s}^{-1},
\end{equation}
where we have assumed stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
calculation purposes we assumed $b=0.95$.  This is challenging, but
for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
with modern spectrographs.  The next viable total transit windows from
Chile occur in January and February of 2021; there are also a few
visible per season from other southern locations.

@@

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be fit simultaneously, which
would greatly constrain any gaussian process model for the
spot-induced RV signal.

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089
%
\tn\ was included on the TESS ``short-cadence'' target list in part
thanks to the Guest Investigator program of G.\ Sacco (G011265).

%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@

%
% The following are entries from Table 1 that are not otherwise cited
% in the text
%
% \nocite{wilson_wasp-4b_2008}
% \nocite{gillon_improved_2009}
% \nocite{winn_transit_2009}
% \nocite{hoyer_tramos_2013}
% \nocite{dragomir_terms_2011}
% \nocite{sanchis-ojeda_starspots_2011}
% \nocite{nikolov_wasp-4b_2012}
% \nocite{ranjan_atmospheric_2014}
% \nocite{huitson_gemini_2017}

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
\clearpage

@@

% \appendix
% \section{Gaia query}
% bounding by 5 stdevns
% Launched query: '
%         select top 10000
%             g.source_id, g.phot_bp_mean_mag, g.phot_rp_mean_mag,
%             g.phot_g_mean_mag, g.parallax, g.ra, g.dec, g.pmra, g.pmdec,
%             g.radial_velocity, g.radial_velocity_error
%         from gaiadr2.gaia_source as g
%         where
%             g.parallax > 5.69
%         and
%             g.parallax < 7.41
%         and
%             g.dec < -58.41
%         and
%             g.dec > -70.33
%         and
%             g.ra > 145.01
%         and
%             g.ra < 175.85
%         and
%             g.phot_g_mean_mag < 18
%         order by
%             random_index

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.43\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    {\it Top:} Mean TESS image of \tn\ over Sector~10, with a
    logarithmic grayscale. The yellow star is the position of \tn.
    Orange circles are neighboring stars with $T<16$ (brighter stars
    are larger). The \texttt{X} and \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  {\it Bottom:} Digitized Sky Survey $R$-band
    image of the same field, with a linear grayscale.  Two stars of
    interest are ``Star A'' and ``Star B'', which were eventually
    excluded as being possible sources of the transits.
		\label{fig:scene}
	}
\end{figure}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.44\textwidth]{f6.pdf}
		}

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
		SOAR HRCam contrast limits derived from point-source
		injection-recovery experiments. A companion dubbed Star A ($\Delta T=4.7$,
	$2.3''$ west) is detected in the autocorrelation function,
	and is also a resolved Gaia source.  It is co-moving with
	\tn, and its parallax and on-sky position imply that it is
	physically separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.
		{\it Middle:} RV measurements, with best-fit instrument offsets
	and jitter terms included.  The expected scatter from starspots
	based on $v\sin i$ and the photometric modulation amplitude is of
	order 300m$\,$s$^{-1}$.
	{\it Bottom:}
	RV measurements phased to the orbital ephemeris of \pn.  The
	planet is not detected.  The black line shows a circular
	Keplerian orbit representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{RVs}
The combined radial velocities from FEROS, CHIRON, and Veloce can be
used to detect massive bound
companions orbiting \tn.  We searched for the presence of planetary and
stellar-mass companions using
\texttt{radvel} \citep{fulton_radvel_2018}.  We assumed circular
orbits, and performed two sets of fits.

@@

\tn\ joins a number of other young planetary systems reported from
TESS, including DS~Tuc~Ab, HIP~67522b, TOI~1726, and AU~Mic~b
\citep{newton_tess_2019,zhou_well_2019,montet_young_2019,rizzuto_tess_2020,mann_tess_2020,plavchan_planet_2020,palle_transmission_2020,addison_youngest_2020,martioli_magnetism_2020,hirano_limits_2020}
Unlike these planets, \pn\ is validated but not yet
confirmed.

@@

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{winn_exoplanet_2010}
\begin{align}
  \Delta V_{\rm RM} \approx \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 21\,{\rm m\,s}^{-1},
\end{align}
where we have assumed stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}, and for
calculation purposes we assumed $b=0.95$.  This is challenging, but
for a 1.9$\,$hr transit of a $V=10.6$ star, a detection could be achieved
with modern spectrographs.  The next viable total transit windows from
Chile occur in January and February of 2021; there are also a few
visible per season from other southern locations.

@@

If the RM measurements prove that the planet
is real, a campaign to measure the mass timed to coincide with
TESS sectors 36 and 37 ({\it i.e.}, from late March to late May of
2021) would significantly ease the extraction of the planetary Doppler
signal.  The reason is that the radial velocities, activity
indicators, and photometry could then be modeled simultaneously, which
would greatly constrain any Gaussian process model for the
spot-induced RV signal.

@@

\input{TOI837_phot_table.tex}

\input{TOI837_rv_table.tex}

%\clearpage
\acknowledgements
\tn\ was included on the TESS ``short-cadence'' target list in part
thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089.
%
%
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@

% \clearpage
% \clearpage

@@
